Models of VOR learning in MHC knockout mice

### 2013-02-08 Notes/VORmodel.tex
talked about less symmetry between gain up & down

The output of the Purkinje cell, and the behavioural output of the animal, will depend on this quantity in some complicated nonlinear way.
Modelling this is far beyond the scope of this work.
Instead we will look at more qualitative features, asking whether learning is slower or faster in some situation compared to another.

@@

With pre-training:
%
\begin{equation}\label{eq:multiKOpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^M - \beta^M(1+2\Delta f)^M}   \,
          \beta^{M/2-1}(1-2\Delta f)^{M/2-1} (1+2\Delta f)^{M/2-1} \\
       &= -4\Delta f q\,\frac{(1-\beta)\beta^{M/2-1}}{1-\beta^M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
Once again, we see that pre-training will speed up learning when $\Delta f$ is small, whereas, if $\Delta f$ is close to $-\half$, pre-training will initially slow down learning.

@@

>>>>

The output of the Purkinje cell, and the behavioural output of the animal, will depend on this quantity in some complicated nonlinear way.
Modelling this is far beyond the scope of this work.
Instead we will look at more qualitative features, asking whether learning is slower or faster in some situation compared to another.
Provided that the nonlinearity is monotonic, these types of questions will not be affected by it.

@@

With pre-training:
%
\begin{equation}\label{eq:multiKOpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1+2\Delta f) - \beta(1-2\Delta f)}
          {(1+2\Delta f)^M - \beta^M(1-2\Delta f)^M}   \,
          \beta^{M/2-1}(1-2\Delta f)^{M/2-1} (1+2\Delta f)^{M/2-1} \\
       &= -4\Delta f q\,\frac{(1-\beta)\beta^{M/2-1}}{1-\beta^M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
Once again, we see that pre-training will speed up learning when $\Delta f$ is small, whereas, if $\Delta f$ is close to $-\half$, pre-training will initially slow down learning.

@@

Now consider what would happen if we did not treat gain-increase and gain-decrease symmetrically.
Let us set $f\pot\dec = f\pot\norm - \overline{\Delta f}$.
Then, \eqref{eq:multiKOpre} becomes
%
\begin{equation}\label{eq:multiKOdiffpre}
\begin{aligned}
  \Phi &= -2\prn{\Delta f + \overline{\Delta f}} q \, \frac{(1+2\overline{\Delta f}) - \beta(1-2\overline{\Delta f})}
          {(1+2\overline{\Delta f})^M - \beta^M(1-2\overline{\Delta f})^M}   \,
          \beta^{M/2-1}(1-2\overline{\Delta f})^{M/2-1} (1+2\overline{\Delta f})^{M/2-1} \\
       &= -2\prn{\Delta f + \overline{\Delta f}} q\,\frac{(1-\beta)\beta^{M/2-1}}{1-\beta^M} + \CO(\Delta f,\overline{\Delta f})^2.
\end{aligned}
\end{equation}
%
We can then look at the wild-type by setting $\beta=1$:
%
\begin{equation}\label{eq:multiWTdiffpre}
\begin{aligned}
  \Phi &= -8\,\overline{\Delta f}\prn{\Delta f + \overline{\Delta f}} q \, 
          \frac{(1-2\overline{\Delta f})^{M/2-1} (1+2\overline{\Delta f})^{M/2-1} }
          {(1+2\overline{\Delta f})^M - (1-2\overline{\Delta f})^M}   \\
       &= -\frac{2\prn{\Delta f + \overline{\Delta f}} q}{M} + \CO(\Delta f,\overline{\Delta f})^2.
\end{aligned}
\end{equation}
%

We can see from these formulae that, if we want pre-training to impair learning in wild-type, but enhance it in the mutant, the important thing is to have \emph{strong pre-training}, not strong training.
Thus, removing the symmetry between gain-increase and gain-decrease will not help with the unrealistic feature of this model -- the fact that pre-training proceeds much faster in the mutant than wild-type.
